---
title: "test_ApiFootball_fetch"
format: html
---

## American football

```{r}
sport <- "american-football"
```

### Games

```{r}
res <- getApiFootball(sport, "games", season = 2023, league = 1)
head(res)
```

### Injuries

```{r}
res <- getApiFootball(sport, "injuries", team = 1)
head(res)
```

### Leagues

```{r}
res <- getApiFootball(sport, "leagues")
head(res)
```

### Odds

```{r}
res <- getApiFootball(sport, "odds", game = "7775")
head(res)
```

### Players

```{r}
res <- getApiFootball(sport, "players", team = 1, season = 2023)
head(res)
```

### Standings

```{r}
res <- getApiFootball(sport, "standings", season = "2023", league = 1)
head(res)
```

### Teams

```{r}
res <- getApiFootball(sport, "teams", league = 2, season = 2023)
head(res)
```

## Baseball

```{r}
sport <- "baseball"
```

### Games

```{r}
res <- getApiFootball(sport, "games", season = 2022, league = 3)
head(res)
```

### Leagues

```{r}
res <- getApiFootball(sport, "leagues")
head(res)
```

### Odds

```{r}
res <- getApiFootball(sport, "odds", season = 2023, league = 22)
head(res)
```

### Standings

```{r}
res <- getApiFootball(sport, "standings", season = 2022, league = 3)
head(res)
```

### Teams

```{r}
res <- getApiFootball(sport, "teams", season = 2022, league = 3)
head(res)
```

## Basketball

```{r}
sport <- "basketball"
```

### Games

```{r}
res <- getApiFootball(sport, "games", season = 2021, league = 201)
head(res)
```

### Leagues

```{r}
res <- getApiFootball(sport, "leagues")
head(res)
```

### Odds

```{r}
res <- getApiFootball(sport, "odds", season = 2023, league = 400)
head(res)
```

### Standings

```{r}
res <- getApiFootball(sport, "standings", season = 2022, league = 48)
head(res)
```

### Teams

```{r}
res <- getApiFootball(sport, "teams", season = 2022, league = 3)
head(res)
```

## Football

```{r}
sport <- "football"
```

### Coachs

```{r}
res <- getApiFootball(sport, "coachs", team = 23)
head(res)
```

### Fixtures

```{r}
res <- getApiFootball(sport, "fixtures", season = 2023, league = 320)
head(res)
```

### Injuries

```{r}
res <- getApiFootball(sport, "injuries", league = 144, season = 2021)
head(res)
```

### Leagues

```{r}
res <- getApiFootball(sport, "leagues")
head(res)
```

### Odds

```{r}
res <- getApiFootball(sport, "odds", league = 61, season = 2023)
head(res)
```

### Players

```{r}
res <- getApiFootball(sport, "players", league = 204, season = 2023)
head(res)
```

### Players / Squads

```{r}
res <- getApiFootball(sport, "players/squads", team = 22)
head(res)
```

### Predictions

```{r}
res <- getApiFootball(sport, "predictions", fixture = 3459)
head(res)
```

### Sidelined

```{r}
res <- getApiFootball(sport, "sidelined", player = 8747)
head(res)
```

### Standings

```{r}
res <- getApiFootball(sport, "standings", season = 2022, league = 3)
head(res)
```

### Teams

```{r}
res <- getApiFootball(sport, "teams", league = 380, season = 2022)
head(res)
```

### Transfers

```{r}
res <- getApiFootball(sport, "transfers", team = 234)
head(res)
```

### Trophies

```{r}
res <- getApiFootball(sport, "trophies", coach = 57)
head(res)
```

## Formula 1

```{r}
sport <- "formula-1"
```

### Circuits

```{r}
res <- getApiFootball(sport, "circuits")
head(res)
```

### Competitions

```{r}
res <- getApiFootball(sport, "competitions")
head(res)
```

### Drivers

```{r}
res <- getApiFootball(sport, "drivers", id = 1)
head(res)
```

### Pitstops

```{r}
res <- getApiFootball(sport, "pitstops", race = 1)
head(res)
```

### Races

```{r}
res <- getApiFootball(sport, "races", season = 2022)
head(res)
```

### Rankings / Drivers

```{r}
res <- getApiFootball(sport, "rankings/drivers", season = 2022)
head(res)
```

### Rankings / Fastest laps

```{r}
res <- getApiFootball(sport, "rankings/fastestlaps", race = 1)
head(res)
```

### Rankings / Races

```{r}
res <- getApiFootball(sport, "rankings/races", race = 1)
head(res)
```

### Rankings / Starting grid

```{r}
res <- getApiFootball(sport, "rankings/startinggrid", race = 1)
head(res)
```

### Rankings / Teams

```{r}
res <- getApiFootball(sport, "rankings/teams", season = 2022)
head(res)
```

### Seasons

```{r}
res <- getApiFootball(sport, "seasons")
head(res)
```

### Teams

```{r}
res <- getApiFootball(sport, "teams")
head(res)
```

## Handball

```{r}
sport <- "handball"
```

### Games

```{r}
res <- getApiFootball(sport, "games", league = 5, season = 2022)
head(res)
```

### Leagues

```{r}
res <- getApiFootball(sport, "leagues")
head(res)
```

### Odds

```{r}
res <- getApiFootball(sport, "odds", league = 54, season = 2023)
head(res)
```

### Standings

```{r}
res <- getApiFootball(sport, "standings", league = 36, season = 2021)
head(res)
```

### Teams

```{r}
res <- getApiFootball(sport, "teams", league = 54, season = 2023)
head(res)
```

## Hockey

```{r}
sport <- "hockey"
```

### Games

```{r}
res <- getApiFootball(sport, "games", league = 53, season = 2022)
head(res)
```

### Leagues

```{r}
res <- getApiFootball(sport, "leagues")
head(res)
```

### Odds

```{r}
res <- getApiFootball(sport, "odds", league = 5, season = 2023)
head(res)
```

### Standings

```{r}
res <- getApiFootball(sport, "standings", league = 36, season = 2021)
head(res)
```

### Teams

```{r}
res <- getApiFootball(sport, "teams", league = 32, season = 2023)
head(res)
```

## NBA

```{r}
sport <- "nba"
```

### Games

```{r}
res <- getApiFootball(sport, "games", league = "vegas", season = 2022)
head(res)
```

### Leagues

```{r}
res <- getApiFootball(sport, "leagues")
head(res)
```

### Players

```{r}
res <- getApiFootball(sport, "players", team = 2, season = 2023)
head(res)
```

### Seasons

```{r}
res <- getApiFootball(sport, "seasons")
head(res)
```

### Standings

```{r}
res <- getApiFootball(sport, "standings", league = "standard", season = 2022)
head(res)
```

### Teams

```{r}
res <- getApiFootball(sport, "teams", league = "standard")
head(res)
```

## Rugby

```{r}
sport <- "rugby"
```

### Games

```{r}
res <- getApiFootball(sport, "games", league = 10, season = 2022)
head(res)
```

### Leagues

```{r}
res <- getApiFootball(sport, "leagues")
head(res)
```

### Odds

```{r}
res <- getApiFootball(sport, "odds", league = 10, season = 2023)
head(res)
```

### Standings

```{r}
res <- getApiFootball(sport, "standings", league = 10, season = 2023)
head(res)
```

### Teams

```{r}
res <- getApiFootball(sport, "teams", league = "10", season = 2022)
head(res)
```

## Volleyball

```{r}
sport <- "volleyball"
```

### Games

```{r}
res <- getApiFootball(sport, "games", league = 53, season = 2022)
head(res)
```

### Leagues

```{r}
res <- getApiFootball(sport, "leagues")
head(res)
```

### Odds

```{r}
res <- getApiFootball(sport, "odds", league = 5, season = 2023)
head(res)
```

### Standings

```{r}
res <- getApiFootball(sport, "standings", league = 36, season = 2021)
head(res)
```

### Teams

```{r}
res <- getApiFootball(sport, "teams", league = 54, season = 2023)
head(res)
```
